---
title: "comparison"
author: "liyiwei"
date: "2019/3/24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
ggplot2 vs. plot_ly


compare plot_ly and ggplot2

Introduction 

plot_ly easily translate 'ggplot2' graphs to an interactive web-based version and/or create custom web-based visualizations directly from R. Once uploaded to a 'plotly' account, 'plotly' graphs (and the data behind them) can be viewed and modified in a web browser. Not only is this web-based user-interface to plotly.js useful for collaborating with others, but it is also useful for completing tasks that are cumbersome to do at the command-line. For instance, annotations can be added to any plot via a point-and-click interface


Plotly and ggplot2 are inherently for different purposes. plotly allows you to quickly create beautiful, reactive D3 plots that are particularly powerful in websites and dashboards. 


```{r}
set.seed(1)
library(plotly)
plot_ly(x = ~rnorm(900), type = "histogram",marker=list(color="purple" , size=20 , opacity=0.5) )
```

```{r}

library(ggplot2)
p = qplot(x = rnorm(900),geom = "histogram",fill="#FF9999", colour="black")
p
```

convert ggplot2 into plotly

An additional benefit of plotly is that you can convert your ggplot() graphs into a plotly object.

```{r}
library(ggplot2)
p = qplot(x = rnorm(1000),geom = "histogram",fill="#E69F00", colour="black")
p
```
Then, invoking the ggplotly(p) command, we see the transformation:
```{r}
ggplotly(p)
```

A draw back of ggplotly() is that if you do refined customization (like putting your legend on the bottom of the graph), ggplotly() doesn???t seem to pick this up by default.
```{r}
# ggplot with legend on the bottom
p = qplot(data = iris, x = Sepal.Width, y = Sepal.Length, geom = "point",color = Species) + theme(legend.position="bottom")
p
```

```{r}
# Plotly doesn't pick up the legend change
ggplotly(p)
```
But since Plotly also saves to an object, you can use the %>% notation to pipe and add additional plotting commands. This is similar to the + operator in ggplot().
```{r}
p = qplot(data = iris, x = Sepal.Width, y = Sepal.Length, geom = "point",color = Species) + theme(legend.position="bottom")
p2 = ggplotly(p) 
# Use the plotly layout() command for legend customization
p2 %>% layout(legend = list(orientation = 'h'))
```

```{r}
#install.packages('ggplot2')
library('ggplot2')
data(diamonds)
```
diamonds in ggplot

```{r}
#install.packages("plotly")
d <- diamonds[sample(nrow(diamonds), 100), ]
```

diamonds in plotly


```{r}
set.seed(100)
ggplot(data = d, aes(x = carat, y = price,colour=carat)) +
  geom_point(aes(text = paste("Clarity:", clarity)), size = 4)
```


```{r}
set.seed(100)
d <- diamonds[sample(nrow(diamonds), 1000), ]
plot_ly(d, x = ~carat, y = ~price, color = ~carat,
        size = ~carat, text = ~paste("Clarity: ", clarity))

```


As we can see, Plotly graphs are interactive. Click on legend entries to toggle traces, click-and-drag on the chart to zoom, double-click to autoscale, shift-and-drag to pan.



Benefits of plotly over ggplot2:

1.Plotly also handles long format.
2.Customizing the layout (plot borders, y axis) is easier.
3.Customizing the legend is easier (in ggplot2 I???ve wanted to remove just one series, which isn???t always easy).
4.Documentation is better in Plotly.
5.Plotly syntax is very intuitive (learning how aes() in ggplot2 works is tricky at first)
6.Plotly also works for Python, Matlab, and Excel, among other languages.
7.It???s very easy to add new series and customize them (one line, one scatter, and one bar, for example)
8.You can use other fonts (which is possible in ggplot2, but I???ve never gotten to work on my Windows machine)
9.You can toggle series on and off by clicking the series name in the legend


Benefits of ggplot2 over plotly:

1.Facet wrapping is very easy in ggplot2. (I think you have to do subplots in plotly.)
2.ggplot2 is probably quicker for exploratory analysis.



